Intentional release of native species undermines ecological stability

### 2022-10-28 rmd/manuscript.Rmd
edit

The reduced fitness of hatchery masu salmon may also play a role in the observed response. Like other salmonids, masu salmon exhibits a life history of "partial migration"; in our study region, the majority of individuals migrate to the ocean and spend approximately one year before spawning, although some males stay in freshwater for their entire life [@moritaLatitudinalVariationGrowth2010; @sahashiMigrationCostsDrive2013; @moritaTemperaturedependentVariationAlternative2014]. It has been shown that ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoostinpress], and such genetic effects may accumulate during the successive generations in captivity [@arakiGeneticEffectsCaptive2007]. Typically, masu salmon are reared in captivity for two to four generations. In light of the 70-year period of the extensive release program, it is conceivable that the "hatchery gene" has spread within the wild populations with measurable fitness declines. This effect may add to negative density dependence to influence community stability.

@@

Under each simulation scenario, we ran `r attr(list_param[[1]], "n_sim")` timesteps of community dynamics for $100$ values of release level $R$ ($0$ to $500$ with an equal interval). We introduced $50$ individuals of each species and allowed them to grow with no intentional release for the first `r unique(list_sim[[1]]$n_warmup)` timesteps (initialization). After the initialization period, we released $R$ individuals of the enhanced species every timestep over the next `r unique(list_sim[[1]]$n_burnin)` timesteps to reach a new equilibrium with the intentional release (burn-in period). We continued the simulation run with intentional release and saved the last `r unique(list_sim[[1]]$n_timestep)` timesteps, which were used to obtain the following summary statistics of the whole community $\sum_i^S N_i$ ($S$: the number of species): the coefficient of variation (CV), the temporal mean ($\mu$), and the SD ($\sigma$). The results of the two-species system were reported in [Supplementary Text].

>>>>

The reduced fitness of hatchery masu salmon may also play a role in the observed response. Like other salmonids, masu salmon exhibits a life history of "partial migration"; in our study region, the majority of individuals migrate to the ocean and spend approximately one year before spawning, although some males stay in freshwater for their entire life [@moritaLatitudinalVariationGrowth2010; @sahashiMigrationCostsDrive2013; @moritaTemperaturedependentVariationAlternative2014]. It has been shown that ocean-migrating adults of hatchery masu salmon show lower return rates to the spawning river [@sahashiWildGenesBoost2022], and such genetic effects may accumulate during the successive generations in captivity [@arakiGeneticEffectsCaptive2007]. Typically, masu salmon are reared in captivity for two to four generations. In light of the 70-year period of the extensive release program, it is conceivable that the "hatchery gene" has spread within the wild populations with measurable fitness declines. This effect may add to negative density dependence to influence community stability.

@@

Under each simulation scenario, we ran `r attr(list_param[[1]], "n_sim")` timesteps of community dynamics for $100$ values of release level $R$ ($0$ to $500$ with an equal interval). We introduced $50$ individuals of each species and allowed them to grow with no intentional release for the first `r unique(list_sim[[1]]$n_warmup)` timesteps (initialization). After the initialization period, we released $R$ individuals of the enhanced species every timestep over the next `r unique(list_sim[[1]]$n_burnin)` timesteps to reach a new equilibrium with the intentional release (burn-in period). We continued the simulation run with intentional release and saved the last `r unique(list_sim[[1]]$n_timestep)` timesteps, which were used to obtain the following summary statistics of the whole community $\sum_i^S N_i$ ($S$: the number of species): the coefficient of variation (CV), the temporal mean ($\mu$), and the SD ($\sigma$). The results of the two-species system were reported in **Supplementary Text**.
